\tool: Revisiting BadUSB with Type-C

### 2021-01-27 WOOT/BadUSBC.tex
Add abstract

\begin{abstract}
\outline{Brief intro of USB protocol}\\
\outline{Brief intro of Rubber Ducky}\\
\outline{What have we done, our contribution}\\
\outline{Our experiment/case study, Attack of shops}\\
\end{abstract}

\begin{IEEEkeywords}
USB;BadUSB
\end{IEEEkeywords}

>>>>

\begin{abstract}
The security of USB protocol has been paid closed attention to, despite its wide usage.
Due to the \textit{trust-by-default} characteristics, USB security has caused serious problems.
For example, a well-known firmware attack, BadUSB, performs malicious operations on the victim hosts through disguising normal USB devices as human interface devices like keyboards and mice.
However, BadUSB suffers from several limitations.
Attackers cannot obtain the status of user interface to conduct precise attacks, and they may be detected by multiple effective countermeasures.
In this work, we extended BadUSB to support the new features of USB Type-C and proposed a multi-mode attack model, \tool.
It can obtain UI status to make attacks more precise and effective, and also bypass many existing defence methods for BadUSB.
To our best knowledge, \tool is the first attack model utilizing USB Type-C.
To validate the usability and effectiveness, we conducted multiple experiments and a user study, in which we got valuable results.
We also proposed reasonable countermeasures for our attack model, which may be inspiring for future research on defence methods.
\end{abstract}

\begin{IEEEkeywords}
USB;BadUSB;
\end{IEEEkeywords}

### 2021-01-27 WOOT/Files/introduction.tex
Add abstract

In this work, we proposed our approach to address the limitations mentioned above and implemented a multi-mode attack model of USB, named \tool.
\tool extends BadUSB to support the features of USB Type-C.
Since USB Type-C is capable to transfer video stream data, \tool could obtain the information of victim's graphical interface during attacks.
Combining it with simulation of traditional HIDs like keyboards and mice, attackers can perform precise attacks.
We did experiments to verify that \tool could also bypass most of the countermeasures for BadUSB since they often rely on interaction with the graphical interface.
Moreover, we implemented multiple attacking modes of USB attacks based on our approach to verify its effectiveness, including scripting, remote control, and privacy extraction.
To improve the efficiency and performance of \tool, we designed a filtering algorithm to preprocess the video data before network transmission.
Moreover, we conducted a series of experiments for each attack mode as well as for different types of devices, including smart phones, personal computers, and tablet computers, to validate the usability of \tool.
We also conducted a user study for attacks in sharing power banks, one of the application scenarios of \tool.
During the user study, we obtained plenty of sensitive data through \tool, since users are usually unconscious of the necessity to check the USB devices they plugged in for security purposes.
After the validation of our attack model, we proposed several defence methods as countermeasures, including external hardware authorization, distrust-by-default, etc.
It is worth noting that we designed a method, called isolated UI rendering, to separate the user interface into sensitive and insensitive layers.
Only content on the insensitive layer will be passed to the insecure driver and thus rendered on external display, which protects content on the sensitive layer.
%\shuqing{Case study, evaluation, notable results.}

We summarize our key contributions as follows:
\begin{itemize}
	\item To our best knowledge, this is the first work to utilize new features of USB Type-C.
	The combination of new support with conventional BadUSB makes attacks more precise and effective.
	\item Our approach can bypass most of the previous countermeasures of BadUSB.
	\item We conducted multiple experiments and a user study to validate the usability and effectiveness of \tool.
	We also proposed several countermeasures for our attack model, which are reasonable and insightful. \fengwei{Add countermeasures, in particular the isolation design.}\shuqing{Isolated UI rendering is added in the last paragraph.}
\end{itemize}

>>>>

In this work, we proposed our approach to address the limitations mentioned above and implemented a multi-mode attack model of USB, named \tool.
\tool extends BadUSB to support the features of USB Type-C.
Since USB Type-C is capable to transfer video stream data, \tool could obtain the information of victim's graphical interface during attacks.
Combining it with simulation of traditional HIDs like keyboards and mice, attackers can perform precise attacks.
We did experiments to verify that \tool could also bypass many countermeasures for BadUSB since they often rely on interaction with the graphical interface.
Moreover, we implemented multiple attacking modes of USB attacks based on our approach to verify its effectiveness, including scripting, remote control, and privacy extraction.
To improve the efficiency and performance of \tool, we designed a filtering algorithm to preprocess the video data before network transmission.
Moreover, we conducted a series of experiments for each attack mode as well as for different types of devices, including smart phones, personal computers, and tablet computers, to validate the usability of \tool.
We also conducted a user study for attacks in sharing power banks, one of the application scenarios of \tool.
During the user study, we obtained plenty of sensitive data through \tool, since users are usually unconscious of the necessity to check the USB devices they plugged in for security purposes.
After the validation of our attack model, we proposed several defence methods as countermeasures, including external hardware authorization, distrust-by-default, etc.
It is worth noting that we designed a method, called isolated UI rendering, to separate the user interface into sensitive and insensitive layers.
Only content on the insensitive layer will be passed to the insecure driver and thus rendered on external display, which protects content on the sensitive layer.
%\shuqing{Case study, evaluation, notable results.}

We summarize our key contributions as follows:
\begin{itemize}
	\item To our best knowledge, this is the first work to utilize new features of USB Type-C.
	The combination of new support with conventional BadUSB makes attacks more precise and effective.
	\item Our approach can bypass many previous countermeasures of BadUSB.
	\item We conducted multiple experiments and a user study to validate the usability and effectiveness of \tool.
	We also proposed several countermeasures for our attack model, which are reasonable and insightful. \fengwei{Add countermeasures, in particular the isolation design.}\shuqing{Isolated UI rendering is added in the last paragraph.}
\end{itemize}
